A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-03 ECCV/paper.tex
Linked related work

In order to be effective, fiducial markers (or simply called, fiducials) need
to be easily detected in the scene.  There are various existing commonly
used fiducial markers 
\cite{NaimarkF02}\cite{ARToolkit02}\cite{Fiala05}\cite{Pitag13}\cite{runetag11}.
These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02}\cite{Fiala05})
or other geometric features arranged in unique spatial patterns
(\cite{NaimarkF02}\cite{Pitag13}\cite{runetag11}).
Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
seen from a quad-copter.  One p roblem, however, is that low-cost quadcopters
often exhibit very quick and erratic motion.  These fast physical movements
results in motion blur in the quadcopters onboard camera.  Such motion blur has an adverse effect the
reconition of fiducial  markers.  This can be seen in Figure \ref{fig:teaser}(b)
where the ARTag cannot be recongized. This is not too surprising as most
fidicuals are not explicitly designed to handle motion blur.  Compounding this
problem is the common problem of dropped video frames from the quadcopters
wireless communication module.   This means that no only is blurring
introduced, but there may be large discountinues in the patterns position due
to missing video frames that makes tracking challenging.

@@

The remainder of this paper is organized as follows.   Section 2 gives an
overview of related work, focused on fiducials as well the related problem of
tracking.  Section X discusses the our design and detection algorithm, by first
examining the performance of existing codes under blur. Section 3 shows several
experiments using quadcopter imagery.  This is followed by a discussion and
summary in Section 4 and 5 respectively.

@@

[For related work, you need to give more context of how these are related to your work. 
This is more of a list of papers and what they do, there relationship is not clear.]

Our work is related to two areas: fiducial markers and
object tracking. We will briefly discuss work done in both areas.
\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}
\end{figure}

The ARToolkit \cite{ARToolkit02}\cite{kato-artoolkit} is well known toolkit in
Augmented Reality system, widely used to find pose of the object on which it is
placed.  Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
bi-tonal system consisting of a square border and
an interior region filled with a 6x6 grid of black or white cells. It proved to
be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
as well as the number of different patterns which can be created.

Concentric rings are reportedly used first by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
have developed ``Circular Data Matrix Fiducial System'', for wide area tracking. ....

@@

Bergamasco et al. \cite{runetag11} developed RUNE-Tag, fiducial marker
system which works under large amount of occlusion. Bergamasco et al. also
designed Pi-Tag \cite{Pitag13}, marker design based on projective
invariants.

The main hurdle in detection of current fiducials is, the detecton of features:
lines in \cite{ARToolkit02}, corners in \cite{Fiala05} while ellipses in
\cite{Cho:2001}, \cite{Cho97fastcolor}, \cite{runetag11} and \cite{Pitag13}.
Such features are very difficult to detect accurately under significant motion
blur. So, under blur, recognition rate of these fiducials is very low.

Fiducial detection in video may be considered as tracking problem where tracked
object is fiducial itself. Visual tracking plays an important role in
surveillance, robotics, human computer interaction, and medical
imaging\cite{Yilmaz:2006}. Yilmaz et al.\cite{Yilmaz:2006} have done survey of
various tracking methods. Most tracking methods
( \cite{Ross:2008} \cite{Wu:2009} \cite{Perez02} \cite{Mei:2009} ) assume image
sequence to be blur free. But in reality, motion blur is inherent part of most
of the videos. Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT)
framework for tracking motion-blurred targets. BLUT is based on the observation
that although motion blurs degrade the visual features of the target, they, at
thde same time, provide useful cues about the movements to help tracking.

@@

Later, we recorded the real data using AR Drone quadcopter. In our experimental
setup, we have kept our fiducial alog with two AR Tags, to compare the
resilience of blur by each fiducial type. We have used ar\_track\_alvar, ROS
Wrapper for ALVAR libray \cite{ros_alvar}, to detect AR Tags from the stream
captured through quadcopter. The comparison of recognition rate shown in Table
\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials(ARTag
as well as ours) is almost 100\%.

@@

\subsubsection{Comparison with BLUT}
We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
and compare it with out result on the same image sequence. From Figure \ref{fig:BLUT_output},
it can be inferred that BLUT is able to track the fiducial when the position of
fiducial doesnot change too much in successive frames. Also, it can be seen
that, once BLUT looses the track of the fiducial, it is not able to recover from
that. But, our algorithm is able to track the fiducial irrespecive of the change
in the position of the fiducial in the image as shown in Figure
\ref{fig:our_output}.

@@

\textbf{Processing Time} :-  Currently our processing time (0.3 seconds per
frame) makes it difficult to do the fiducial detection in real-time. When we have
done the code profiling, we found that Gabor filter takes most of the time (0.03
-- 0.04 seconds perorientation). As we are applying Gabor filter along eight
orientations, we should think of some optimized way to do filtering.
Alternatively, some replacement for Gabor filter needs to be find out.

\textbf{False Negatives} :- We found that sometime our detection algorithm is
failed do recognize our fiducial with binary code ``0'' when there is large
amount of blur. This is the reason behing low recognition rate of ``00''
coded fiducial compared to that of our other fiducial patterns. When we
investigated the problem, we found that, if there is too much blur, the
innermost ring is not detected along the direction perpandicular to blur
direction. This problem can be resolved by increasing radius of innermost ring.

>>>>

In order to be effective, fiducial markers (or simply called, fiducials) need
to be easily detected in the scene.  There are various existing commonly
used fiducial markers 
\cite{NaimarkF02}\cite{ARToolkit02}\cite{Fiala05}\cite{Pitag13}\cite{runetag11}.
These typically take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02}\cite{Fiala05})
or other geometric features arranged in unique spatial patterns
(\cite{NaimarkF02}\cite{Pitag13}\cite{runetag11}).
Figure \ref{fig:teaser} shows an example of the popular ARTag\cite{Fiala05} as
seen from a quad-copter.  One problem, however, is that low-cost quadcopters
often exhibit very quick and erratic motion.  These fast physical movements
results in motion blur in the quadcopters onboard camera.  Such motion blur has an adverse effect the
reconition of fiducial  markers.  This can be seen in Figure \ref{fig:teaser}(b)
where the ARTag cannot be recongized. This is not too surprising as most
fidicuals are not explicitly designed to handle motion blur.  Compounding this
problem is the common problem of dropped video frames from the quadcopters
wireless communication module.   This means that no only is blurring
introduced, but there may be large discountinues in the patterns position due
to missing video frames that makes tracking challenging.

@@

The remainder of this paper is organized as follows.   Section 2 gives an
overview of related work, focused on fiducials as well the related problem of
tracking.  Section 3 discusses the our design and detection algorithm, by first
examining the performance of existing codes under blur. Section 4 shows several
experiments using quadcopter imagery.  This is followed by a discussion and
summary in Section 5 and 6 respectively.

@@

Our work is related to two areas: fiducial markers and
object tracking. We will briefly discuss work done in both areas.

\textbf{Fiducials} :- Some of fiducial designs are shown in Figure
\ref{fig:previous_work}.

\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}
\end{figure}

Intitially there were attempts to design a fiducial embeded with two dimensional
barcode inside a rectangular grid. One of the examples of such fiducial is,
ARToolkit\cite{ARToolkit02}, well known toolkit in Augmented Reality(AR) system. 
Kato et al.\cite{kato-artoolkit} have deomstrated the use of ARToolkit to find
the pose in cideo conferencing system. Many AR applications used ARToolkit
due to its simplicity and efficiency.

Fiala et al. \cite{Fiala05} developed a fiducial termed, ARTag, which is a
bi-tonal system consisting of a square border and an interior region filled
with a 6x6 grid of black or white cells. The improvement in ARTag compared
ARToolkit was detection of coreners instead of detection of lines to find
possible pattern. It proved to be more efficient than \cite{ARToolkit02} in
terms of marker recognition rate as well as the number of different patterns
which can be created. But, drawback of ARTag is, under significant amount of
motion blur, corners can not be detected, resulting in non-recognition of tag.

There were also attempts to use circular patterns instead of rectangular, as
the projective transfomration of circles, i.e. conics, are invariant with
resepctive to point of view of camera\cite{runetag11}. Also, such patterns are
mostly distingushable from background and generally can not be missed.

Concentric rings are reportedly used first by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings instead of
black and white rings\cite{concentric} to increase possible number of fiducials.
These multicolor rings are used in wide area tracking in large scale
applications.

Naimark et al. \cite{NaimarkF02} have combined concentric rings and 2D bar code
in their fiducial named, Circular Data Matrix. It was beneficial in terms of
easy detection of fiducial as well as more number of fiducial patterns.

All of these fiducials are not recognizable under occlusion.
Bergamasco et al. \cite{runetag11} have divided fiducial into number of
circular dots, and arranged them in circular fashion, named as RUNE-Tag.
RUNE-tags are reportedly detectable even if 50\% of fiducial area is occluded.
Bergamasco et al. have devloped another fiducial, named as Pi-Tag
\cite{Pitag13}, using cross-ratio concept. As cross-ratio is projective
invariant, the detection of Pi-tag is easier than other tags. Also, compared
to RUNE-tag, it uses remarkably less number of circular dots (12 dots instead of
minimum of 43 dots), still reconisable under occlusion.

But again problem with circular fiducials is, it is very difficult to detect
ellipses accurately under significant motion blur. So, under blur, recognition
rate of these fiducials is very low.

@@

\textbf{Tracking}:-
Fiducial detection in video may be considered as tracking problem where tracked
object is fiducial itself. Visual tracking plays an important role in
surveillance, robotics, human computer interaction, and medical
imaging\cite{Yilmaz:2006}. Yilmaz et al.\cite{Yilmaz:2006} have done survey of
various tracking methods.

Most tracking methods( \cite{Ross:2008} \cite{Wu:2009} \cite{Perez02}
\cite{Mei:2009} ) assume image sequence to be blur free. But in reality, motion
blur is inherent part of most of the videos. Wu et al.\cite{Wu:2011} have
developed BLUr-driven Tracker (BLUT) framework for tracking motion-blurred
targets. BLUT is based on the observation that although motion blurs degrade
the visual features of the target, they, at thde same time, provide useful cues
about the movements to help tracking.

@@

Later, we recorded the real data using AR Drone quadcopter. In our experimental
setup, we have kept our fiducial along with two AR Tags, to compare the
resilience of blur by each fiducial type. We have used ar\_track\_alvar, ROS
Wrapper for ALVAR libray \cite{ros_alvar}, to detect AR Tags from the stream
captured through quadcopter. The comparison of recognition rate is shown in
Table \ref{tab:recongition_accuracy}. Classification accuracy of all fiducials(ARTag
as well as ours) is almost 100\%.

@@

\subsubsection{Comparison with BLUT}
We have used sample image sequence to test the performance of BLUT\cite{Wu:2011}
and compare it with our result on the same image sequence. From Figure
\ref{fig:BLUT_output}, it can be inferred that BLUT is able to track the fiducial when the position of
fiducial doesnot change too much in successive frames. Also, it can be seen
that, once BLUT looses the track of the fiducial, it is not able to recover from
that. But, our algorithm is able to track the fiducial irrespecive of the change
in the position of the fiducial in the image as shown in Figure
\ref{fig:our_output}.

@@

\textbf{Processing Time} :-  Currently our processing time (0.3 seconds per
frame) makes it difficult to do the fiducial detection in real-time. When we have
done the code profiling, we found that Gabor filter takes most of the time (0.03
-- 0.04 seconds per orientation). As we are applying Gabor filter along eight
orientations, we should think of some optimized way to do filtering.
Alternatively, some replacement for Gabor filter needs to be find out.

\textbf{False Negatives} :- We found that sometime our detection algorithm is
failed do recognize our fiducial with binary code ``00'' when there is large
amount of blur. This is the reason behing lower recognition rate of ``00''
coded fiducial compared to that of our other fiducial patterns. When we
investigated the problem, we found that, if there is too much blur, in Gabor
output, the innermost ring is unable to give any response along the direction
perpandicular to blur direction. This problem can be resolved by increasing
radius of innermost ring, reducing effect of blur on the innermost ring.
